% This is a demonstration file distributed with the
% Lecturer package (see lecturer-doc.pdf).
%
% You can recompile the file with a basic TeX implementation,
% using pdfTeX or LuaTeX with the plain format.
%
% The reusable part ends somewhere around line 300.
%
% Author: Paul Isambert.
% Date: July 2010.

\documentclass{article}

\usepackage{luatex85}
\usepackage{luaotfload}
\RequirePackage{shellesc}
\usepackage{minted}
\usepackage{lecturer}
\usepackage{fontspec}
\usepackage{graphics}
% \usepackage{xcolor}

% \input luatex85.sty
% \input luaotfload.sty
% \input lecturer
%\setsansfont{Gill Sans MT}

\usemintedstyle{tango}

\setmonofont{Fira Mono}
\setmainfont{Fira Sans}

\font\maintitlefont    = {name: League Gothic} at 100pt
\font\slidetitlefont   = {name: Reklame Script DEMO} at 30pt
% \font\slidetitlefont = {name: Fira Sans} at 20pt
\font\subtitlefont     = {name: Reklame Script DEMO}
\font\mainsubtitlefont = {name: Reklame Script DEMO} at 50pt
\font\titlefont        = {name: Fira Sans}
\font\tenrm={name: Fira Sans} at 10pt

% \newcolor{lightgrey}{grey}{.85}
% \newcolor{darkgrey}{grey}{.7}
% \newcolor{darkred}{rgb}{.6 0 0}
% \newcolor{bluenavy}{rgb}{.12 .14 .24}
% \newcolor{coral}{rgb}{.93 .29 .36}

% \newcolor{tropiteal}{html}{00A8C6}
% \newcolor{tealdrop}{html}{40C0CB}
% \newcolor{whitetrash}{html}{F9F2E7}
% \newcolor{atomicbikini}{html}{AEE239}
% \newcolor{feebleweek}{html}{8FBE00}

\newcolor{tropiteal}{rgb}{0 168 198}
\newcolor{tealdrop}{rgb}{64 192 203}
% \newcolor{whitetrash}{rgb}{249 242 231}
%\newcolor{atomicbikini}{rgb}{174 226 57}
\newcolor{feebleweek}{rgb}{143 190 0}


\newcolor{atomicbikini}{rgb}{.68 .89 .22}
% \newcolor{green}{rgb}{.56 .75 .0}
% \newcolor{darkred}{rgb}{.0 .66 .78}
\newcolor{tropiteal}{rgb}{.0 .66 .78}
% \newcolor{coral}{rgb}{.97 .94 .90}
\newcolor{whitetrash}{rgb}{.97 .94 .90}


\newcolor{maintitlebackground}{rgb}{.0 .66 .78} % tropiteal
\newcolor{maintitleforeground}{rgb}{.97 .94 .90} % whitetrash
\newcolor{mainsubtitleforeground}{rgb}{.97 .94 .90} % whitetrash
\newcolor{titleforeground}{rgb}{.68 .89 .22} % atomic bikini
\newcolor{slidebackground}{rgb}{.97 .94 .90} % whitetrash
\newcolor{itemcolor}{rgb}{.0 .66 .78} % tropiteal


\def\Subtitle{A Shapeless Primer}


\setparameter job:
  mode           = presentation % The handout is ready, just turn it on.
  author         = "A Shapeless Primer"
  title          = "BE LIKE WATER"
  date           = "Some centuries B.C."
  fullscreen     = true
  autofullscreen = true
  font           = \tenrm % Plain TeX's default, but must be specified
                          % to set it back after a \step with another font.

\setparameter slide:
  everyslide    = \everyslide
  % hsize         = ".6\pdfpagewidth"
  top           = 76pt
  bottom        = 42pt
  areas*        = "title subtitle date"
  bookmarkstyle = italic
  baselineskip  = 12pt
  topskip       = \baselineskip
  width         = 16cm
  height        = 9cm
  background    = slidebackground
  % left          = 1cm % default 2cm
  % right         = 1cm

\def\everyslide{%
  \position{titlebar}\slidetitle
  }
% \def\dobutton#1#2{%
%   #1[push]{\rlap#2\buttonborder}\hskip1em
%    }

%
% Top and bottom bars.
%

\setarea{topleft topright bottomleft bottommiddle bottomright}
  height = 18pt



\setarea{titlebar}
  vshift     = 35pt
  left       = 3em
  height     = 40pt
  % background = lightgrey
  foreground = titleforeground
  topskip    = 30pt
  hpos       = fr
  font       = \slidetitlefont


%
% The title slide.
%
\setslide{titleslide}
  areas      = "title subtitle"
  bookmark   = false
  hpos       = rr
  everyslide = {}
  background = maintitlebackground

\setarea{title}
  hshift*    = 1cm
  vshift     = 2.5cm
  height     = 45pt
  topskip    = 50pt
  foreground = maintitleforeground
  top        = 1em
  %frame      = "width=.2em, corner=round, color=darkgrey"
  hpos       = rr
  font       = \maintitlefont

\setarea{subtitle}
  hshift*    = 1cm
  vshift     = 6cm
  height     = 28pt
  topskip    = 20pt
  foreground = mainsubtitleforeground
  frame      = "width=.2em, corner=round"
  hpos       = rr
  font       = \mainsubtitlefont

\setarea{date}
  hshift*    = 5.5cm
  vshift     = 9cm
  height     = 22pt
  topskip    = 10pt
  background = white
  foreground = black
  top        = 5pt
  frame      = "width=.5em, corner=bevel, color=lightgrey"
  hpos       = rr


%
% For the appendices.
% We remove the math area instead
% of redefining \everyslide.
%
\setslide{appslide}
  areas* = "math title author date"

%
% Default step.
%
\setparameter step:
  everyvstep = "\quitvmode\llap{\itemsymbol\kern.5em}"
  vskip = 18pt

%
% Foreground math.
%
\setstep\emptystep
  everyvstep everyhstep = {}
  vskip hskip = 0pt

%
% Item symbols.
%
\newsymbol\itemsymbol[.6em,padding=0pt]
  {color itemcolor, + 1 0, + 0 1, + -1 0, fill,}
\newsymbol\mathsym[.5em,padding=0pt]
  {color itemcolor,
  + 1 .5, + -1 .5, fill,}
\newsymbol\backsym[.5em,padding=0pt]
  {color itemcolor, move 1 0, + -1 .5, + 1 .5, fill,}
%
% Navigation to the appendices.
%
\def\Back#1{%
  \presentationonly{\usecolor{darkred}{\gotoB{#1}{\subtitlefont\backsym\kern.3em Back}}}%
  }
\def\To#1{%
  \presentationorhandout{\usecolor{darkred}{\gotoA{#1}{\subtitlefont\mathsym\kern.3em See why}}}
    {{\usecolor{darkred}{\subtitlefont\mathsym\kern.3em(See Appendices)}}}%
  }
%
% And some structure.
%
\def\section#1{%
  \def\sectiontitle{#1}%
  \createbookmark[nosubmenutext,open]{.5}{#1}%
  }


% \endinput
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                             %
% UNCOMMENT THE PREVIOUS LINE TO USE THIS FILE AS A TEMPLATE, %
% OR REMOVE EVERYTHING BELOW.                                 %
%                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\titleslide

\position{title}\Title
%\position{author}[0cm,-1.7cm]{\it\usecolor{black}{A Casual Talk By}}
\position{subtitle}\Subtitle
\position{date}\Date

\endtitleslide





\section{Demonstration}

\begin{slide}[Some source code]
  \inputminted[fontsize=\small]{kotlin}{source/fizzbuzz.kt}
\end{slide}

\slide[A simple assumption]

\step Some say the square root of 2 isn't rational.
\step Suppose
 were.

\step[A] Then we could write it as this, where $a$ and $b$ are
integers without a common factor.
\To{app1}

\step[B] But then we can also write this.
\step[C] And this.
\step[D] And finally this.
\step Which means that $a^2$ is even.

\endslide



\slide[Its consequences]


\step[visible="true"] So what?
\step So $a$ is even. Because only even numbers produce even squares.
\To{app2}

\step[A] Being even means being expressible in the form $2k$, where $k$ is
any integer.
\step[B] And $(2k)^2$ square gives $4k^2$.

\step[C] Let's simplify.
\step Thus $b^2$ is even.
\step And $b$ is too.

\endslide



\slide[The problem]

% \domath7 A {}

\step[visible=true] And but so we said $a$ and $b$ have no common factor.

\step If both are even they do have a common factor: 2.
\step Which is absurd.

\step Thus, our basic assumption is false.
\step[A] There are no such $a$ and $b$.

\step The square root of 2 is irrational.
\step Too bad.

\endslide





\section{Appendices}



\appslide[All fractions are reducible]


\step[visible=true]
Suppose $c\over d$ is a rational number. If c and d have no common
factor, then $a=b$ and $b=d$. If they have a common factor,
divide both by their greatest common divisor. The result
is $a\over b$, with no common factor.

\vskip\baselineskip
\Back{app1}

\endappslide



\appslide[An even square has an even root,scale=true]

\step[visible=true]
An even number, by definition, is expressible
in the form $2k$, where $k$ is any integer.
On the other hand, an odd number is expressible
by $$2k+1$$
Thus the square of an odd number is
$$(2k+1)^2$$
i.e. $$4k^2+4k+1$$
i.e. $$2\times2(k^2+k)+1$$
which is of the form $2k+1$
with $2(k^2+k)$ as $k$.
Hence, an odd number produces an odd square,
and thus if a square is even its root is even too.

\vskip\baselineskip
\Back{app2}

\step[visible=true] You might have noticed
that this page is slightly scaled to accommodate
its content to the slide's declared {\usecolor{darkred}{vsize}}
parameter. Actually, it is scaled because I stretch this
paragraph so as to have too much content. Which is kind
of paradoxical. Or just opportunistic.

\endappslide

\end{document}
